Mechanized Reasoning about a Capability Machine

### 2019-10-18 prisc-2020/paper.tex
removed appendix
future work

In our case, however, calls are not always well-bracketed (since the capability machine includes general jump instructions).
\citeauthor{skorstengaardESOP18} distinguishes between well-bracketed and non well-bracketed calls by using notions of public- and private future worlds, following \cite{dreyer_neis_birkedal_2012}.
Iris invariants do not make such a distinction and thus invariants alone are not sufficient for our purposes.
Instead we explicitly define notions of public and private future world relations, and use these notions to distinguish between well-bracketed and non well-bracketed calls.
We use these relations in combination with Iris' higher-order ghost state, which allow us to save a predicate by associating it to a unique ghost name.
Using that unique name, we are then able to refer to the saved predicate somewhere else, and apply it to
an appropriate future world argument.

@@

@@

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

>>>>

In our case, however, calls are not always well-bracketed (since the capability machine includes general jump instructions).
\citeauthor{skorstengaardESOP18} \cite{skorstengaardESOP18} distinguishes between well-bracketed and non well-bracketed calls by using notions of public- and private future worlds, following \cite{dreyer_neis_birkedal_2012}.
Iris invariants do not make such a distinction and thus invariants alone are not sufficient for our purposes.
Instead we \textit{explicitly} define notions of public and private future world relations, rather than relying on Iris' \textit{implicit} future world, and use these notions to distinguish between well-bracketed and non well-bracketed calls.
We use these relations in combination with Iris' higher-order ghost state, which allow us to save a predicate by associating it to a unique ghost name.
Using that unique name, we are then able to refer to the saved predicate somewhere else, and apply it to
an appropriate future world argument.

@@

In the future we plan to finish the remaining details of the implementation, then use it as a starting point to prove full abstraction of a compiler from a high level language to our capability machine. Furthermore, it can also be used as a starting point for exploring different kinds of capabilities.

@@

% %% Appendix
% \appendix
% \section{Appendix}

% Text of appendix \ldots
